A Transdiciplinary approach to developing a 3D spectral numerical coastal-flow model based on passive macroalgal rafting phenenomea to shed light on ambient and stochastic dispersal and connectivity of nearshore and offshore marine communities  around the coast of South Africa

### 2019-10-08 literature_review.Rmd
lit review touch ups

---
title: A Transdiciplinary approach to developing a 3D spectral numerical coastal-flow model based on passive macroalgal rafting phenenomea to shed light on ambient and stochastic dispersal and connectivity of nearshore and offshore marine communities  around the coast of South Africa
author: "Ross Coppin"
output:
  word_document:
    fig_caption: yes
    toc: yes
  pdf_document:
    toc: yes
bibliography: ref_lit_review.bib
---

```{r include=FALSE}
library(png)
library(grid)
library(rticles)
```

>>>>

---
title: A Transdiciplinary approach to developing a 3D spectral numerical coastal-flow model based on passive macroalgal rafting phenenomea to shed light on ambient and stochastic dispersal and connectivity of nearshore and offshore marine communities  around the coast of South Africa
author: "Ross Coppin"
output:
  pdf_document:
    toc: yes
  word_document:
    fig_caption: yes
    toc: yes
bibliography: ref_lit_review.bib
---

```{r include=FALSE}
library(png)
library(grid)
```
